---
title: "Functions the package can use and examples"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Functions the package can use and examples}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(F25mooketsi)
```

# Introduction

This package contains R functions designed mainly to interpret data, with some displaying visual representations and others returning keys statistics about the data.

## Function 1 - myncurve

Plots a normal curve with mean mu and standard deviation sigma, shades the area from the left up to a, and returns the numerical value of that shaded probability.

```{r, fig.width=6, fig.height=4, out.width="80%"}
myncurve(mu=10,sigma=5, a=6)
```

## Function 2 - myboot2

Performs a bootstrap on the sample x using the statistic fun, runs it for iter iterations, plots the bootstrap distribution, and returns the confidence interval, the statistic used, the original sample, and the bootstrap estimates (Xstat).

```{r, fig.width=6, fig.height=6, out.width="80%"}
myboot2(10000,x=rnorm(25,mean=25,sd=10))
```

## Function 3 - ntickets

Computes the optimal number of tickets to sell for an overbooking scenario, produces two plots of the objective function (discrete and continuous), and returns a list containing the optimal discrete and continuous solutions (nd, nc) along with N, p, and gamma).

```{r, fig.width=7, fig.height=10, out.width="90%"}

ntickets(400,0.02,0.95)
```

## Function 4 - mybinplot

Simulates iter runs of a Binomial(n, p) process and displays the resulting distribution as a bar plot.

```{r, fig.width=6, fig.height=4, out.width="80%"}
mybinplot(100,10,0.7)
```

